CRUSE to Safe Cycling in Ireland

### 2023-10-17 paper.qmd
Update title page

```{r}
#| include: false
#| eval: false
library(tidyverse)
remotes::install_dev("tmap")
library(tmap)
# Save title page (1st page of paper.pdf):
system("pdftk _site/paper.pdf cat 1 output _site/title_page.pdf")
# Combine cv.pdf with visions.pdf:
system("pdftk _site/cv.pdf _site/visions.pdf cat output _site/cv_and_visions.pdf")
```

>>>>

```{r}
#| include: false
#| eval: false
library(tidyverse)
remotes::install_dev("tmap")
library(tmap)
# Save title page (1st page of paper.pdf):
system("pdftk paper.pdf cat 1 output _site/title_page.pdf")
# Combine title page and cover-letter.pdf:
system("pdftk _site/cover-letter.pdf _site/title_page.pdf cat output _site/cover_letter_full.pdf")
browseURL("_site/cover_letter_full.pdf")
# Combine cv.pdf with visions.pdf:
system("pdftk _site/cv.pdf _site/visions.pdf cat output _site/cv_and_visions.pdf")
```
